---
title: "homework6"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

library(rvest)
library(httr)
library(p8105.datasets)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Data clean
```{r}
baby_birthweight_df=read.csv("data/birthweight.csv") %>% 
  select(-pnumlbw,-pnumsga) %>%
  mutate(babysex=as.factor(babysex),frace=as.factor(frace),mrace=as.factor(mrace),malform=as.factor(malform)) %>% 
  filter(!menarche<5) %>% 
  filter(!fincome<5) %>% 
  mutate(babysex=factor(babysex, levels = 1:2, labels = c("female", "male"))) %>%     mutate(mrace=factor(mrace,levels=1:5,labels=c("White","Black","Asian","Puerto Rican","Other"))) %>% 
  mutate(malform=factor(malform,levels = 0:1,labels=c("absent","present"))) %>% 
  mutate(frace=factor(frace,levels = 1:9,labels=c("White","Black","Asian","Puerto Rican","Other","","","Other","Unkown"))) %>% 
  mutate(mrace=fct_infreq(mrace)) %>% 
  select(babysex,bhead,blength,bwt,gaweeks,mrace)

colSums(is.na(baby_birthweight_df))
baby_birthweight_df %>% skimr::skim_without_charts()
```

There is a sense that baby's head circumference at birth is positively correlated to baby's birth weight and at the genetic level,mother's race plays a important role in baby's birth weight.

```{r}
baby_birthweight_df %>% 
  ggplot(aes(x=bhead,y=bwt,color=mrace)) + geom_point(alpha=0.4) 

baby_birthweight_df %>% 
  ggplot(aes(x=bhead,y=bwt)) + geom_point(alpha=0.4) + facet_wrap(.~mrace)

baby_birthweight_df %>% 
  ggplot(aes(x=mrace,y=bwt)) + geom_violin(alpha=0.4)
```

The plots above sort of align with the hypothesis that baby's head circumference at birth and mother's race are two factors underlying baby's birthweight.


The model I propose is:
```{r}
my_fit = lm(bwt ~ bhead  +  mrace,data=baby_birthweight_df )

broom::tidy(my_fit) %>% 
  select(term,estimate,p.value) %>% 
  mutate(term=str_replace(term,"mrace","Mother's race:")) %>% 
  knitr::kable()

```

```{r}
baby_birthweight_df %>% 
  modelr::add_residuals(my_fit) %>% 
  modelr::add_predictions(my_fit) %>% 
  select(bwt,bhead,mrace,resid,pred) %>% 
  ggplot(aes(x=pred,y=resid)) + geom_point(alpha=0.3) 
```

Two other models 

```{r}
fit2=lm(bwt~blength + gaweeks,data=baby_birthweight_df)
summary(fit2)

fit3=lm(bwt~bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex,data=baby_birthweight_df)
summary(fit3)

```

Compare 3 models

```{r}
cv_df=
  crossv_mc(baby_birthweight_df,100) %>% 
  mutate(
    train=map(train,as.tibble),
    test=map(test,as.tibble)
  ) %>% 
  mutate(my_fit = map(.x = train, ~lm(bwt ~ bhead + mrace, data = .x )),
    fit2 = map(.x = train,~lm(bwt~blength + gaweeks, data = .x)),
    fit3 = map(.x = train,~lm(bwt~bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    my_fit_rmse = map2_dbl(my_fit, test, ~rmse(model = .x, data = .y)),
    fit2_rmse = map2_dbl(fit2, test, ~rmse(model = .x, data = .y)),
    fit3_rmse = map2_dbl(fit3, test, ~rmse(model = .x, data = .y))
  ) %>%
  select(ends_with("rmse")) %>% 
  pivot_longer(
    everything(),names_to = "model",values_to = "rmse"
  ) %>% 
  ggplot(aes(model,rmse)) + geom_violin()

cv_df
```

According to the plot, the second model, which is third model(using head circumference, length, sex, and all interactions (including the three-way interaction) between these) has the best fitness.


## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
set.seed(1)
boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    model = map(strap, ~lm(tmax~tmin, data = .x)),
    glance = map(model, broom::glance),
    results = map(model, broom::tidy)
  ) %>% 
  unnest(glance) %>% 
  select(.id, r.squared, results) %>% 
  unnest(results) %>%
  mutate(
    term=str_replace(term,"\\(Intercept\\)","Intercept")
  ) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
 group_by(.id) %>% 
  summarise(intercept = max(Intercept, na.rm = TRUE),
            tmin = max(tmin, na.rm = TRUE),
            r.squared = mean(r.squared)) %>% 
  mutate(
    result = log(intercept*tmin)
  )
boot_straps %>% 
  ggplot(aes(x = r.squared)) + geom_density()+
  labs(title = 'distribution of r_squared')
  
boot_straps %>% 
  ggplot(aes(x = r.squared)) + geom_density()+
  labs(title = 'distribution of log(beta0*beta1)')
```

Both r_squared and log(beta0*beta1) follows normal distribution, which align with central limit theorem.


```{r}
boot_straps %>% 
  summarize(
    r_squared_ci_lower = quantile(r.squared, 0.025), 
    r_squared_ci_upper = quantile(r.squared, 0.975),
    result_ci_lower = quantile(result, 0.025), 
    result_ci_upper = quantile(result, 0.975)) %>% 
  knitr::kable(caption = '95% CIs')
```











